%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}

% Default font is the helvetica postscript font
\usepackage{helvet}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{Aadil Bhatti}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{601 S. 6th St\\Champaign, IL 61820\\}
\address{abhatti2@illinois.edu\\847.363.0768\\linkedin.com/in/aadilbhatti}

% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{University of Illinois at Urbana-Champaign}, Urbana-Champaign, IL\\
{\sl Bachelor of Science}, Mathematics and Computer Science, May 2017\hfill GPA:
3.30
\\
Minor in Chemistry
\\
\\
\textbf{Courses}: Data Structures, Computer Architecture, System Programming,
Algorithms \& Models of Computation, Numerical Methods, Programming Languages
\& Compilers

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
\textbf{Linux in the Browser}:
An in-browser System Programming environment including a C compiler and working
Linux terminal. Worked on the project under Professor Lawrence Angrave during
Spring 2016 - Fall 2016. Role was to make C compiler / terminal more portable
for other developers to use and develop a Jupyter-like frontend as a use case.

\par
\textbf{Chimr}:
Built a ``smart'' doorbell at WildHacks 2015 which alerts the homeowner via text
message that someone is at the door. Won \textbf{Best Use of Twilio API}. Potential
uses include notification sent to parents to let them know that children have arrived
home from school. Built with \textbf{Python/Flask, Twilio API, and Arduino}.

\par
\textbf{Rapsheet}:
Built a full-stack web application to track \& analyze Twitter sentiment about music
albums on Spotify. Goal was to search for trends between Twitter user opinions and
Spotify album popularity. Made with \textbf{Python/Django, Spotify API, Alchemy API, and D3.js}.

\par
\textbf{Watdo}:
Built a full-stack web application to track local events in town of Dekalb, IL during
HuskieHacks 2015; won \textbf{Best Civic Sector Project}. Goal was to collect events
from multiple sources across the town and aggregate them for people who are not familiar
with the town to look at. Made with \textbf{Meteor.js}.

%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}

\textbf{Languages}: Java, Python, C++, C, Haskell, Ruby, MATLAB
\\
\textbf{Web Development}: HTML, CSS, JavaScript, Django, Ruby on Rails, SQL, Node,
                          React, Meteor, jQuery, Knockout, D3
\\
\textbf{Mobile Development}: Android (Java, Android Studio),
iOS (Swift, XCode)
\\
\textbf{Other Tools}: Git/GitHub, Amazon Web Services (EC2, S3, DynamoDB, Lambda),
Arduino, Alexa Skills Kit (Amazon Echo)
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}
\employer{\textbf{Capital One}}
\location{Urbana-Champaign, IL}
\dates{February 2016 - Present}
\title{\textbf{Software Engineering Intern}}
\begin{position}
Examined the utility of the Juju Charms service orchestration tool and its potential
use within Capital One. Goal was to determine if Juju is a feasible tool for deploying
applications to Amazon Web Services without needing extensive background knowledge as
to how AWS works. Built simple web application in Django and deployed with Juju to
illustrate how tool works and how to use it.
\end{position}

\employer{\textbf{PillSense}}
\location{Chicago, IL}
\dates{May 2015 - Present}
\title{\textbf{Software Engineer}}
\begin{position}
PillSense is a healthcare startup devoted to tracking patient prescription adherence
data in order address prescription abuse. We are currently designing a web application,
a mobile application, and a sensor to track the weights of pill bottles. My role in the
startup was, as the sole software engineer in a team of five, to build the web application
for which care providers can access patient data.

\end{position}
%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
% \section{INTERESTS}
% Web development, artificial intelligence, machine learning, numerical computing,
% system programming
%-------------------------------------------------------------------------------
\end{resume}
\end{document}
